Croder \\ Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Added a picture of the wizard
Issue #9
Added text for the wizard part
Again, for issue #9

\section{Stackexchange code review characteristics}
\section{Interface with StackExchange}
\section{Review management in the IDE}
\section{Crowd sourced peer review creation}
\section{Tying review outcomes to the code}
\section{Preliminary user study}
\section{Sketches}
\section{Conclusion}

>>>>

\section{Stackexchange code review characteristics}
\section{Interface with StackExchange}
\section{Review management in the IDE}

\section{Crowd sourced peer review creation}

For creating of the task we chose to implement a wizard. One of the main features is that you can ask
for \emph{structured} code review. The user can select a criteria under which code review should be
performed (performance, design, readability etc.). This helps reviews in keeping a focus on a given task.
Also, to make it easier for them to understand the code, we allow the users to add a small note regarding
the purpose and content of each code snippet. The code snippets are selected directly from the IDE.

In figure~\ref{fig:wizard} we show the design approach we took. While it is a bit crude, it does offer all
the features and presents the structured approach to creating the task. It is worth mentioning that the user
has the option to add a general comment at an earlier stage in the wizard.

\begin{figure}[hbt]
	\includegraphics[width=\columnwidth]{wizard.png}
\caption{Adding comments for each snippet}
\label{fig:wizard}
\end{figure}

\section{Tying review outcomes to the code}
\section{Preliminary user study}
\section{Sketches}
\section{Conclusion}
